A preliminary constraint grammar for Russian

### 2015-03-24 2015-nodalida-ruscg/ruscg.tex
add f-score
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59022 72bbbca6-d526-0410-a7d9-f06f51895060
add two types of eval
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59023 72bbbca6-d526-0410-a7d9-f06f51895060
section assignments
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59024 72bbbca6-d526-0410-a7d9-f06f51895060
more comments
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59292 72bbbca6-d526-0410-a7d9-f06f51895060
table
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59293 72bbbca6

\section{Review of literature}
% ROB + FRAN
% different CGs 
% faroese
% estonian
%

@@

\section{Ambiguity in Russian}

@@

@@

\subsection{Disambiguation rules}

@@

\section{Development process}

@@

\begin{table*}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    \textbf{Domain} & \textbf{Tokens} & \textbf{Precision} & \textbf{Recall} & \textbf{Ambig. solved} \\
    \hline
    Wikipedia       & 7,857      & 0.506        & 0.996    & 44.92\%  \\
    News            & 642        & 0.471        & 0.990    & 41.60\%  \\
    Literature      & 1,652      & 0.473        & 0.984    & 42.95\%  \\
    \hline
    Total           & 10,150     & 0.498        &  0.994   &  44.39\% \\
    \hline
  \end{tabular}
  \caption{Results for the test corpora.}
\end{table*}

@@

@@

% func analysis
% dep analysis

>>>>

\section{Review of literature}
% ROB Russian POS tagging

% FRAN
% different CGs 
% faroese
% estonian

State-of-the-art morphological analysis in Russian is primarily based on finite-
state technology \cite{Nozhov-03,Segalovich-03}.\footnote{Machine-learning approaches have also been successfully applied to Russian, most notably by \newcite{sharoff08lrec-mocky}.} Almost without exception, all large-scale morphological transducers of Russian are based on the
forward-looking \emph{Grammatical Dictionary of Russian} \cite{Zaliznjak-77}.
This dictionary gives fine-grained morphological specifications for more than
100~000 words, including inflectional endings, morphophonemic alternations, 
stress patterns, exceptions, and idiosyncratic collocations.
We base our work on the recently developed [anonymous] morphological transducer, which is also based on Zaliznjak's dictionary (Author, 2015).\footnote{The [anonymous] transducer is implemented using a two-level 
morphology \cite{Koskenniemi-84}, and can be compiled using either {\tt xfst}
\cite{Beesley.Karttunen-03} or {\tt hfst} \cite{hfst-11}} This finite-state transducer (FST) generates all possible 
morphosyntactic readings of each wordform, regardless of its frequency or probability. Because Russian is a relatively highly inflected language, broad coverage is important, but widespread homonymy leads to the generation of many spurious readings, as discussed in Section~\ref{ambiguity} below. Because of this, one of the foundational steps in Russian natural language processing is morphosyntactic disambiguation, or \emph{snjatie omonimii}.

 -- and our Constraint 
Grammar\footnote{Implemented using vislcg3 constraint grammar parser
(http://beta.visl.sdu.dk/cg3.html).}
\cite{Karlsson-90,Karlsson.Voutilainen.ea-95} then removes
some readings based on syntactic context.

@@

\section{Ambiguity in Russian} \label{ambiguity}

% ROB
% homography

% sketch out the different kinds of ambiguity and show what percentage they are 
% give examples
% describe stress related ambiguity, e.g. where orthographic form is the same but diff. stress

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|}
    \hline
    \textbf{Type}     & \textbf{\% all tokens} & \textbf{\% ambig. tokens} \\
    \hline
    Intraparadigmatic & 59.0                   & 90.9   \\
    Incongruent       & 27.7                   & 42.7   \\ 
    Congruent         & 1.20                   & 1.8    \\ 
    \hline
  \end{tabular}
  \caption{Types of ambiguity}
  \label{table:ambiguity}
\end{table}

% numbers not perfect, e.g. лицо should be 'cong.' but will turn up as 'intra.'

@@

% FRAN

@@

% det/prn (e.g. pos... их, я, мой)
% 'over'generation (e.g. all dets get all gen/nbr/case combinations)

\subsection{Disambiguation rules}
%FRAN

@@

\section{Development process}
%FRAN

@@

\subsection{Intrinsic}
%FRAN

\begin{table*}
  \centering
  \begin{tabular}{|l|r|r|r|r|r|}
    \hline
    \textbf{Domain} & \textbf{Tokens} & \textbf{Precision} & \textbf{Recall} & \textbf{F-score} & \textbf{Ambig. solved} \\
    \hline
    Wikipedia       & 7,857      & 0.506        & 0.996    & 0.671 & 44.92\%  \\
    Literature      & 1,652      & 0.473        & 0.984    & 0.638 & 42.95\%  \\
    News            & 642        & 0.471        & 0.990    & 0.638 & 41.60\%  \\
    \hline
    \textbf{Average}& 10,150     & 0.498        &  0.994   & 0.663 & 44.39\% \\
    \hline
  \end{tabular}
  \caption{Results for the test corpora.}
\end{table*}

@@

\subsection{Extrinsic}
% ROB accent placement task

@@

% ROB
% FRAN
% func analysis
% dep analysis
